%!TEX root = main.tex
\cleardoublepage
\thispagestyle{empty}
\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgments}
\chapter*{Acknowledgments}

Everything leading up to this thesis would not have been possible without the continuous support of many people. Here, I would like to thank these people and I may have forgot some.

First, I would like to thank Dr. Roman Poeschl and Dr. Thibault Frisson who made me start in this research area. It was such a great experience and gave the will to pursue my studies in particle physics and detector development. Moreover, they gave me the opportunity to go to CERN and advised me to go to DESY.

I would like to thank Dr. Mark Terwort who supervised my work during the DESY summer school and without whom I may not have started a thesis at DESY. I would like to thank Dr. Felix Sefkow who has his door always open for questions and advices. I profited so much from your guidance and knowledge about calorimetry, physics and politics. I would like to give a special thank to Prof. Dr. Erika Garutti who endorsed me as her student and gave me advices through my thesis.

I would like to give a special thanks to Dr. Katja Kr\"uger, this thesis would not have been finished without your enormous efforts in proof-reading presentations, abstracts, papers and this thesis. I am thankful for all the ideas, the questions, the guidance and the discussions we had through all my thesis. Your tremendous knowledge about physics and past experiments (especially about H1) gave me more interest in particle physics and shaped me as a young scientist. I would like to give an exceptional thank to Dr. Marcel Stanitzki who proof-read my thesis twice and give me wonderful comments and advices about it. I am also greatly thankful for the talks we had and the joy that you bring with you.

I would like to thank many other people from the FLC group for their advices, teaching and administrative help over these years: Ties Behnke, Karsten B\"usser, Mathias Reinecke, Shaojun Li, Remi \'Et\'e, Andrea Schr\"ader, Karsten Gadow, Jenny List, Moritz and many others that may have left in the meantime.

The AHCAL group people, especially Jiri, Ambra, Lan, Oskar, Ali, Ambra, Coralie, Benjamin and Yuan made my work in this group unforgettable and very entertaining some time, especially during shifts at DESY or CERN.

I would like to thank Alex, Alexey, Hayk, Sergey and Volodymyr who sparkled in me the interest for bouldering which help me to stay in shape and keep my head cool most of the time. I would like to thank many other friends: Ksenia, Artur L., Artur T., Ali H., Natali, Nataliia K., Nataliia Z., Olga, Miro, that made my work during the last 4 years a wonderful experience.

Last but not least, I would like to especially thank my girlfriend, Mengqing Wu, who supported me through the last hard month of my thesis. You are the best thing that happened in my life. I am deeply grateful for all your advices and the strength you gave me. I love you. Finally, to my grandparents that unfortunately past away before this thesis and to my aunt, who always supported me in every way for the last 27 years and I would not have achieved my goals without your support.
